\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{11}

### 2015-09-15 ICRA2016/bandits_docs/includes/abstract.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

\begin{abstract}
Advances in computing and massive datasets of images and human speech have produced recent results that surpass decades of past research on analytic methods..
This raises the question: can Big Data and Cloud Computation produce analogous advances in robot grasping and manipulation?
We develop an algorithm based on a Multi-Armed Bandit model with correlated rewards and show that our algorithm can leverage a large dataset of prior grasps and 3D object models to reduce the number of samples needed for robust grasp planning.
To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps along with the probability of force closure of each grasp under uncertainty in object pose, gripper pose, and friction coefficient.
We use Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between objects and apply MV-CNNs to indexing similar objects for grasp planning at scale.
We implement Dex-Net 1.0 using the Google Cloud Platform with a system that can simultaneously run up to 1,500 virtual machines, reducing experiment runtime by up to 1000$\times$.
Experiments suggest that robust grasp planning is up to 3.5$\times$ faster than Thompson sampling without prior data and that average grasp quality scales with the size of the dataset when the MV-CNN returns geometrically similar objects.
We also explore sensitivity of our algorithm to similarity metrics and pose and friction uncertainty levels for test objects.
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

>>>>

\begin{abstract}
This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and cloud computation on robust grasp planning. 
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
Experiments suggest that prior data can speed robust grasp planning by a factor of up to 3 and that average grasp quality increases with the number of similar objects in the dataset.
We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
Code, data, and additional information can be found at: \TODO{Url}.
\end{abstract}

### 2015-09-15 ICRA2016/bandits_docs/includes/algorithm.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
The Dex-Net 1.0 algorithm (see below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.
We acknowledge alternatives for grasp selection on each iteration~\cite{kroemer2010combining, laskey2015bandits, montesano2012active, oberlin2015autonomously}, but use Thompson sampling to study the scaling effects for a fixed selection method.

@@

\subsection{Belief Distribution Model}
\seclabel{belief}
Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
Our Bayesian MAB algorithm works by maintaining a belief on the $P_F$ for each grasp that is updated with every new force closure evaluation, assigning increasingly high probability to the true $P_F$. 
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution on the Bernoulli parameter $\theta_{j}$ using a Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits}, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net 1.0.
CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
In our context, two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.

@@

We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
Our first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, our second feature map $\phi_{2} = \eta$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
The bandwidths are hyperparameters of the algorithm that are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.

>>>>

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
The Dex-Net 1.0 algorithm (see below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from the uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
Finally, we rank the grasps in $\Gamma$ by the maximum $p$-lower confidence bound, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
We use Thompson sampling to study the scaling effects for a fixed grasp selection method and plan to study other methods based on confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.

@@

\subsection{Belief Distribution Model}
\seclabel{belief}
Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$. 
The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.

@@

We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similiary map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.

### 2015-09-15 ICRA2016/bandits_docs/includes/conclusion.tex
Made Ken's changes and added a bit more experimental detail. Committing before some final updates to figures with new experiments

\section{Discussion and Future Work}
\seclabel{conclusion}
We developed a Multi-Armed Bandit algorithm based on correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models, each labelled with up to 250 grasps and the probability of force closure of each.
For efficient indexing of similar objects in Dex-Net, we used multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art deep learning method of object classification, trained on milliions of images and thousands of 3D object examples.
Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.

Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We plan to add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}, and study the selection of a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
We plan to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

>>>>

\section{Discussion and Future Work}
\seclabel{conclusion}
We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning.
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models and Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects.
In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
Experiments suggest that prior data can speed robust grasp planning by a factor of 3 and that average grasp quality increases with the number of similar objects in the dataset.
We reported on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.

In future work, we will develop metrics to pre-compute grasps that adequately "cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
We will also explore how Deep Learning~\cite{krizhevsky2012imagenet} can be used in other parts of a grasp planning pipeline, for example to recognize object pose and shape from images~\cite{aubry2015understanding}, to learn grasp and object features robust to shape variation using prior evaluations from bandit algorithms, and perhaps even to determine motor torques based on images and precomputed grasps~\cite{levine2015end}.
We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).

%We developed the Dex-Net 1.0 algorithm using a Multi-Armed Bandit model with correlated rewards to reduce the number of samples required to plan robust parallel-jaw grasps by leveraging prior grasps and 3D object models.
%To study scaling effects, we introduced the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 3D object models and 2.5 million parallel-jaw grasps, and MV-CNNs~\cite{aubry2015understanding, su2015multi} to efficiently index similar objects.
%Our experiments suggest that increasing the amount of prior knowledge of objects and the quality of grasps on each object enables up to a $10\times$ speedup in the time to compute a grasp with high probability of force closure for a new object, and also suggest that convergence is fastest when the object has a set of geometrically similar nearest neighbors in the database.
%
%One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
%Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
%We are also interested in an end-to-end approach that integrates research on deep learning to map directly from images to motor torques that control a grasp.
%To do so, we will use supervision from the data in Dex-Net to study prediction of object identity and pose directly from depth images~\cite{aubry2015understanding} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
%%We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface and to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.
%
%In future work, we will also add grasp and object data to Dex-Net, such as more 3D models, task constraints, the outcomes of physical trials, or human annotations.
%%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
%%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
%We will also explore additional analytic grasp metrics to Dex-Net such as cages, different grasp selection policies such as Gittins indices, and extensions to plan a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
%We will also include uncertainty in object shape resulting from noisy point clouds~\cite{mahler2015gp} to future models.
%Our goal is to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.
%
